### 2017-11-21 manuscript.rmd
piping to pdf

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F, include=F}
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

>>>>

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F, include=F}
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim) %>% pdf("density_sex_sim")
```

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)%>% pdf("palpons_sim")
```
